Blum axioms and nondeterministic computation of functions

### 2016-05-17 paper.tex
paper.tex: Mention the existence of alternative approaches to "nondeterministic funcions".

@@

Call $\FNP$ the class of all functions computable in polynomial time,
under our definition.
A language $L$ is $\NP$-complete if both $L \in \NP$
and every language in $\NP$ reduces to $L$;
that is, for every language $L' \in \NP$,
there is a polynomial-time computable function $f$
such that, for every $x$,
\begin{equation*}
    x \in L' \text{ if and only if } f(x) \in L.
\end{equation*}
(We are using Karp reductions here \cite[p.~42]{AroraBarak2009}.)
If we rephrase in terms of the characteristic functions $1_L$ and $1_{L'}$,
of $L$ and $L'$, respectively,
we have $1_{L'}(x) = 1_L(f(x))$ for all $x$.
We will generalize specifically this equation to define $\FNP$-completeness.

>>>>

\section{Our approach}
\label{sec:our-approach}

The mathematical definition of function
requires it to return a value for all elements of its domain,
and to return a single value in all cases.
In this paper,
we will try to associate nondeterministic computation
with \emph{partial} recursive functions;
that is,
functions that are only defined for some elements in its domain.
(Strictly speaking,
these objects are not ``functions'';
but we will allow for this abuse of nomenclature.
If the partial function is defined everywhere,
we will call it a \emph{total} function, for contrast.)
In general,
we cannot demand a function resulting from a computation to be total
because the computation may not halt.

Since nondeterministic computation returns several values,
to associate it with functions we need to either restrict what things define a function
or to somehow extract a single value from all these branches of computation.
It is important to note that this is not the only approach available in the literature.
Complexity classes like $\ComplexityFont{NPVM}$
(see, for example, the paper of Selman~\cite[p.~359]{Selman1994})
are defined using \emph{multivalued functions},
which are allowed to return several values for a single input.
Another approach is to use \emph{function problems} associated to problems in $\NP$,
where the machine is required to return any certificate for the given instance,
or to reject the input if it is not in the language;
this yields the class $\FNP$~\cite[p.~229]{Papadimitriou1994}.
We will not consider these approaches here;
in particular, we will define $\FNP$ differently below.

@@

Call $\FNP$ the class of all functions computable in polynomial time,
under our definition\footnote{
    As noted in section~\ref{sec:our-approach},
    this definition is different
    from the one given by Papadimitriou~\cite[p~229]{Papadimitriou1994}.
}.
A language $L$ is $\NP$-complete if both $L \in \NP$
and every language in $\NP$ reduces to $L$;
that is, for every language $L' \in \NP$,
there is a polynomial-time computable function $f$
such that, for every $x$,
\begin{equation*}
    x \in L' \text{ if and only if } f(x) \in L.
\end{equation*}
(We are using Karp reductions here \cite[p.~42]{AroraBarak2009}.)
If we rephrase in terms of the characteristic functions $1_L$ and $1_{L'}$,
of $L$ and $L'$, respectively,
we have $1_{L'}(x) = 1_L(f(x))$ for all $x$.
We will generalize specifically this equation to define $\FNP$-completeness.
